\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2019

% ready for submission
% \usepackage{neurips_2019}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2019}

% to compile a camera-ready version, add the [final] option, e.g.:
     \usepackage[final]{neurips_2019}

% to avoid loading the natbib package, add option nonatbib:
%     \usepackage[nonatbib]{neurips_2019}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{Microsoft-Recommenders: Best Practices for Production-Ready Recommendation Systems}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  Name \\
  Microsoft, Azure Global \\
  2 Kingdom St, London W2 6BD, UK \\
  \texttt{name@microsoft.com} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

\begin{document}

\maketitle

\begin{abstract}
Recommendation systems have become one of the most widely applied areas of machine learning in modern business and 
have attracted great interest in machine learning research. Recommendation algorithms are involved in a large percentage of 
consumer purchases in today's e-commerce production systems. We present {\em Microsoft-Recommenders},  
an open-source Github repository for helping researchers, developers and non-experts in general to select, prototype, train and
bring to production a variety of state-of-the-art recommendation algorithms.
A focus of this repository is on {\em best practices} in development of recommendation systems and Python software for machine learning.
We have also incorporated learnings from our experience with recommendation systems in production, in order to enhance ease of use; speed of 
implementation and deployment; ease of evaluation; scalability and performance. 
The repository has also received contributions from the broader community of researchers and data science practitioners. 
In turn, the repository is a useful aid to anyone in this community and simplifies development and application of recommendation algorithms.
\end{abstract}

\section{Introduction}

\input{intro}

\section{Overall Approach and Technologies}

\input{overall}

\section{Coding Guidelines}

\input{coding}

\section{System Design}

\input{system}

\section{Structure of the Repository}

Microsoft-Recommenders is based on best practices for building recommendation systems, which have been learned from application with production-ready systems.
As a consequence, we have followed an {\em end-to-end} approach, which is not limited to just the training of an algorithm, but encompasses the following components, typical in a recommendation pipeline:

\begin{itemize}
\item Data preparation: Preparing and loading data for each recommender algorithm
\item Model: Building models using various classical and deep learning recommender algorithms such as Alternating Least Squares (ALS) or eXtreme Deep Factorization Machines (xDeepFM).
\item Evaluate: Evaluating algorithms with offline metrics
\item Model Select and Optimize: Tuning and optimizing hyperparameters for recommender models
\item Operationalize: Operationalizing models in a production environment on Azure
\end{itemize}

Several utilities are provided in \url{https://github.com/microsoft/recommenders/blob/master/reco_utils} to support common tasks such as loading datasets in the format expected by different algorithms, evaluating model outputs, and splitting training/test data. Implementations of several state-of-the-art algorithms are provided for self-study and customization in one's own applications.

\subsection{Data Preparation}

\input{dataprep}

\subsection{Recommendation Algorithms}

\input{algos}

\subsection{Offline Evaluation}

\input{evaluation} 

\subsection{Model Selection}

\input{tuning}

\subsection{Operationalization}

\input{o16n}

\subsection{Utilities}

\input{utils}


\subsection{Conclusions - Learnings}

\input{learnings}


\subsubsection*{Acknowledgments}


\section*{References}



\end{document}
